`r params$doc_title`

### 2022-11-17 scripts/MSc.Rmd
added performance measures

est %>% 
  mutate(OR=exp(estimate), CI.lower=exp(estimate-se.estimate),CI.upper=exp(estimate+se.estimate)) %>%  
  kable(digits=3, caption = "MR Results for GBC (outcome) using genetic variants as instrumental variables for BMI") %>% 
  kable_classic(full_width = FALSE, html_font = "Cambria")
```

@@

## initialize
nsim <- 25
est <- tibble(no_sim = 1:nsim)
#est <- matrix(NA, 
#              nrow = nsim, 
#              ncol = 2*length(n)  # theta_sim and theta_se_sim
#              ) 
#colnames(est) <- c(paste0("theta_sim_", n), paste0("theta_se_sim_", n))

@@

   # PERFORM MR_analysis
   mr.obj = MendelianRandomization::mr_input(
         bx = sim_dat$beta.bmi_sim_norm, 
         bxse = sim_dat$se_update_BMI, 
         # outcome
         by = sim_dat$beta.gbc_sim_norm, 
         byse = sim_dat$se_update_GBC, 
         snps = sim_dat$SNP,
         exposure = "Body mass index",
         outcome = "Gallbladder Cancer"
       ) 
   # CONMIX (as reference)
   res = MendelianRandomization::mr_conmix(mr.obj)
   colname_theta <- paste0("theta_sim_", n[i])
   colname_theta_se <- paste0("theta_se_sim_", n[i])
   ## store results
   est[k, colname_theta] <- res$Estimate
   CIlength = res$CIUpper-res$CILower
   if (length(CIlength)>1) print("conmix multimodal")
   est[k, colname_theta_se] <- sum(CIlength)/1.96/2  ## Caution: this may be problematic 
   rm(res)
 }
 rm(se_update_BMI, se_update_GBC)
 print(paste0("|||-----------------------Run finished for sample size: ", n[i], " -----------------------|||"))
}

@@

saveRDS(est, paste0(Sys.Date(), "_est.rds"))
```

>>>>

est %>% 
  mutate(OR=exp(estimate), CI.lower=exp(estimate-se.estimate),CI.upper=exp(estimate+se.estimate)) %>%  
  kable(digits=3, caption = "MR Results for GBC (outcome) using genetic variants as instrumental variables for BMI") %>% 
  kable_classic(full_width = FALSE, html_font = "Cambria")

saveRDS(est, paste0("../output/Rdata/", Sys.Date(), "_est.rds"))
```

@@

## initialize
nsim <- 25
est_sim <- tibble(no_sim = 1:nsim)
#est_sim <- matrix(NA, 
#              nrow = nsim, 
#              ncol = 2*length(n)  # theta_sim and theta_se_sim
#              ) 
#colnames(est_sim) <- c(paste0("theta_sim_", n), paste0("theta_se_sim_", n))

@@

   # PERFORM MR_analysis
   mr.obj = MendelianRandomization::mr_input(
         bx = sim_dat$beta.bmi_sim_norm, 
         bxse = sim_dat$se_update_BMI, 
         # outcome
         by = sim_dat$beta.gbc_sim_norm, 
         byse = sim_dat$se_update_GBC, 
         snps = sim_dat$SNP,
         exposure = "Body mass index",
         outcome = "Gallbladder Cancer"
       ) 
   # CONMIX (as reference)
   res = MendelianRandomization::mr_conmix(mr.obj)
   colname_theta <- paste0("theta_sim_", n[i])
   colname_theta_se <- paste0("theta_se_sim_", n[i])
   ## store results
   est_sim[k, colname_theta] <- res$Estimate
   CIlength = res$CIUpper-res$CILower
   if (length(CIlength)>1) print("conmix multimodal")
   est_sim[k, colname_theta_se] <- sum(CIlength)/1.96/2  ## Caution: this may be problematic 
   rm(res)
 }
 rm(se_update_BMI, se_update_GBC)
 print(paste0("|||-----------------------Run finished for sample size: ", n[i], " -----------------------|||"))
}

@@

saveRDS(est_sim, paste0("../output/Rdata/", Sys.Date(), "_est_sim.rds"))
est_sim <- readRDS(file = "../output/Rdata/2022-11-15_est_sim.rds")
```

### Performance Metrics

```{r}
bias <- function(thetaobs,theta) mean(thetaobs)- theta
mse <- function(thetaobs, theta) mean((thetaobs-theta)^2)

bias(thetaobs = est_sim$theta_sim_50000, theta = est$estimate[est$mr_methods == "conmix"])
mse(thetaobs = est_sim$theta_sim_50000, theta = est$estimate[est$mr_methods == "conmix"])
```
